\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\RequirePackage{tikz}
\usetikzlibrary{arrows}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

\newcommand{\cvtag}[1]{%
  \tikz[baseline]\node[anchor=base,draw=body!30,rounded corners,inner xsep=1ex,inner ysep =0.75ex,text height=1.5ex,text depth=.25ex]{#1};
}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Brian Fung}}\\
	Melbourne, Australia
	\vspace{0.1cm}
	\\
\end{center}

\begin{center}
	\vspace{0.01cm}
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  0422 285 751 \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ brianf.iwnl@gmail.com \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/fungiwnl \hfill \raisebox{-0.2\height}{\Large \faGlobe} \ \ https://fungiwnl.com
\end{center}

\hrule
\vspace{-1em}
\subsection*{\Large Professional History}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	\headerrow
	{\textbf{Kmart}}
	{\textbf{Melbourne}}
	\headerrow
	{\emph{Software Test Engineer}}
	{\emph{September 2021 -- Present}}
	\begin{itemize*}
      \item Quality Engineer for the customer account and identity team (MyAccount).
	  \item Lead maintainer for Kmart Online's test automation and performance testing initiatives cross teams (MyAccount, Cart, Availability).
      \item Wired up the existing automation suite, to run tests within the Buildkite CI/CD pipeline and set up additional cron jobs to run the tests.
      \item Uplifted the sunsetted automation framework from synchronous Webdriver.io to asynchronous Webdriver.io: adding linting, logging, email testing capability, and all around improvements of the stability of the test suite.
      \item Currently, migrating functional tests to run against stubs. So far, greatly reducing test run time: 50 tests that took over 30 minutes to run down to 3 minutes.
      \item Currently, migrating the Jmeter performance tests to K6 to uplift the performance testing workflow

	\end{itemize*}
       \vspace{0.2cm}
            \cvtag {Typescript/Javacript} \cvtag{Github Actions} \cvtag {Jmeter/K6}  \cvtag{Webdriver.io} \cvtag{Wiremock} \cvtag{Docker} \cvtag{AWS}
            \vspace{0.4cm}
        
		
	\item
	      \headerrow
	      {\textbf{Two Bulls}}
	      {\textbf{Melbourne}}
	      \headerrow
	      {\emph{Senior QA Engineer}}
	      {\emph{September 2019 -- August 2021}}
	      \begin{itemize*}
	        \item Quality Engineer responsible for the test strategy, test creation, test execution and automation in agile environments for responsive web and native mobile applications.
            \item Provided DevOps support: created and maintained numerous CI/CD pipelines for native iOS and Android mobile applications and Game Engines.
	      \end{itemize*}
	      \headerrow
	      {\emph{QA Engineer}}
	      {\emph{May 2017 -- September 2019}}
	      \begin{itemize*}
	      	\item Responsible for test creation, execution and automation in both agile and waterfall environments on desktop and mobile based applications. 
	        \item Created a CI pipeline for a cross platform video distribution platform for the core, windows and native mobile application streams.
	      	\item Developed a script to install test builds for on-premise iOS and Android mobile devices for testing, greatly reducing the time to set up testing activities. 
	      \end{itemize*}

            \vspace{0.2cm}
            \cvtag {Javascript} \cvtag{Cypress}  \cvtag{Appium}  \cvtag{Github Actions}  \cvtag{Jenkins} \cvtag{Gitlab} \cvtag{AWS}
            \vspace{0.4cm}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Featured Projects}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em

	\item
	      \headerrow
	      {\textbf{Release.me - Web}}
	      {\textbf{}}
	      \begin{itemize*}
	      	\item An off the plan real estate platform for developers and buyers.  
                \item Developed an automation test suite using Cypress that ran as part of the CI/CD pipeline
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {Javascript} \cvtag{Cypress} \cvtag{Codepipelines}
            \vspace{0.4cm}
        
	
	\item
	      \headerrow
	      {\textbf{Scouts Australia - Web}}
	      {\textbf{}}
	      \begin{itemize*}
	      	\item A digital web transformation to uplift the Scouts analogue paper system.
                \item Provided DevOps support: created a pipeline for running the regression automation test suite to support the teams ongoing automation efforts.
                \item Contributed to the ongoing development off the test automation suite. 
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {Javascript} \cvtag{Cypress} \cvtag{Cloudformation} \cvtag{Codepipelines}
            \cvtag{Cloudformation} \cvtag{Lambda} \cvtag{S3} \cvtag{Cloudfront} \cvtag{Route53}
            \vspace{0.4cm}

          \headerrow                                                                                       
          {\textbf{Ufonik - Mobile}}
          {\textbf{}}
          \headerrow
          {\emph{June 2021 -- July 2021}}
          {\emph{}}
          \begin{itemize*}
          	\item A tik-tok esque native mobile application designed for musicians and content creators.
            \item Developed a regression test suite including visual snapshot tests in XCUITest that ran as part of CI/CD 
            \item Provided DevOps support: creating and maintaining the Buddybuild CI/CD pipeline for the iOS mobile app and integrated automation tests to run within the pipeline. 
	      \end{itemize*}
           \vspace{0.2cm}
           \cvtag {Swift} \cvtag{iOS} \cvtag{Buddybuild CI} \cvtag{XCUITest} \cvtag{Snapshot tests}
           \vspace{0.4cm}

          \headerrow                                                                                       
          {\textbf{21 Cricket - Mobile}}
          {\textbf{}}
          \headerrow
          {\emph{May 2021 -- June 2021}}
          {\emph{}}
          \begin{itemize*}
          	\item A fitness and training mobile app focused on cricket for Michael Clark. 
            \item Provided DevOps support: set up the code signing, created and maintained the CI/CD pipeline using Github Actions.
            \item Developed component widget tests in flutter.
	      \end{itemize*}
           \vspace{0.2cm}
           \cvtag {Dart} \cvtag{Flutter} \cvtag{Github Actions} \cvtag{Fastlane}
           \vspace{0.4cm}

	      \headerrow
	      {\textbf{Service Victoria - Mobile}}
	      {\textbf{}}
	      {\emph{April 2017 -- July 2021}}
	      {\emph{}}
	      \begin{itemize*}
	      	\item A mobile app to check-in throughout Victoria and securely store and share your identity including things like licences and permits.
            \item Provided DevOps support: created and maintained the Bitrise CI/CD pipelines, automating deployment of release builds to the Google Play and App store. 
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {iOS} \cvtag{Android} \cvtag{Bitrise CI}
            \vspace{0.4cm}
	      
	      \headerrow
	      {\textbf{Beyond Now - Mobile }}
	      {\textbf{}}
	      \headerrow
	      {\emph{Jan 2018 -- September 2021}}
	      {\emph{}}
	      \begin{itemize*}
	      	\item Beyond blue's suicide safety planning app that assists you to create your own suicide safety plan; a plan to keep you safe when experiencing suicidal thoughts.
            \item Provided DevOps support: created and maintained the CI/CD pipeline for the iOS and Android native mobile apps. 
            \item Developed the automation suite using Appium
            \item Created a smoke testing suite that ran on an AWS stack (Cloudwatch, Codepipelines, Device Farm) managed by Cloudformation templates.
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {Python} \cvtag{Appium} \cvtag{Buddybuild} \cvtag{Bitrise CI} \cvtag {Cloudwatch} \cvtag{Cloudformation} \cvtag{Lambda} \cvtag{S3} \cvtag{Route53} \cvtag{Codepipelines} \cvtag{Lambda} \cvtag{S3}
            \vspace{0.4cm}
	      
	      \headerrow
	      {\textbf{Wiggles/Sesame Street Yourself/Oddbods oddlife - Mobile games}}
	      {\textbf{}}
	      \headerrow
	      {\emph{Jan 2018 -- Dec 2018}}
	      {\emph{}}
	      \begin{itemize*}
	      	\item An engaging mobile Augmented Reality experience enabling children to sing and play along with their favorite screen characters.
            \item Provided DevOps support: created and maintained the CI/CD pipeline for the Game Engine team using Gitlab. 
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {iOS} \cvtag {Android} \cvtag {Gitlab} \cvtag{Buddybuild CI} \cvtag {Bitrise CI}
            \cvtag {Locust} \cvtag {Terraform}
            \vspace{0.4cm}
	      
	      \headerrow
	      {\textbf{Verizon Digital Kiosk - Embedded system}}
	      {\textbf{}}
	      \headerrow
	      {\emph{2017 -- 2018}}
	      {\emph{}}
	      \begin{itemize*}
	      	\item Communications hubs that connect people to important and useful information - providing weather and emergency alerts, maps and local community information about transit, restaurants, businesses and events.
            \item Provided DevOps support: maintained the existing Bitrise CI/CD pipeline for the android applications developed for the Digital Kiosk.
            \item Developed a regression automation suite using bats (bash automation testing framework).
            \item Created a script to download test builds from Bitrise (CI) to install on the Digital Kiosk towers for testing, greatly reducing the set up time for regularly occuring testing activities.
	      \end{itemize*}
            \vspace{0.2cm}
            \cvtag {Android} \cvtag {Bash} \cvtag{Bitrise CI}
            \vspace{0.4cm}

         \headerrow
         {\textbf{Vividas - Video Player SDK}}
         {\textbf{}}
         \headerrow
         {\emph{2017 -- 2018}}
         {\emph{}}
         \begin{itemize*}
         	\item Cross platform video distribution and playback service for mobile and desktop.  
            \item Provided DevOps support: maintaining the Jenkins build master and slaves and the CI pipeline to build the core video engine and the native iOS and Android mobile applications. 
            \item Migrated away from the use of Jenkins jobs to using a declarative Jenkins pipeline that could be versioned controlled
         \end{itemize*}
         \vspace{0.2cm}
         \cvtag {iOS} \cvtag{Android} \cvtag{Windows app} \cvtag{Jenkins}
         \vspace{0.4cm}

	      
\end{itemize}
	      
\hrule
\vspace{-1em}
\subsection*{\Large Technical Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Programming Languages:}
	      Typescript/Javascript, Python, Bash, Golang, \LaTeX
	\item \textbf{Test Automation:}
	    Webdriver.io, Playwright, Cypress, Cucumber, Supertest, Jest, Storybook, XCUITest, Appium,  Wiremock, Axe
	\item \textbf{CI/CD} 
        Github Actions, Jenkins, Gitlab, Bitrise, Buildkite, Buddybuild, Bitbucket pipelines
	\item \textbf{Performance:} 
        Jmeter, K6, Locust, Lighthouse
    \item \textbf{Amazon Web Services (AWS):} 
        EC2, ECS, S3, IAM, Cloudwatch, Lambda, Cloudformation, Cloudfront, Route53, Codepipelines
    \item \textbf{Containers/IaC}
        Docker, AWS CDK, Cloudformation
    \item \textbf{Quality:}
        Test planning, Progression, Regression, Smoke/Sanity, UAT, PVT, Performance, Compatibility, Accessibility, User testing
    \item \textbf{API testing:} 
        REST, GraphQL
    \item \textbf{Monitoring:} New Relic, Sumologic
    \item \textbf{Version control:} 
        Git, Github, Gitlab, Bitbucket
    \item \textbf{Development tools:}
        Neovim, Tmux, Alacritty, Vscode
    \item \textbf{Operating Systems:} 
        Linux (Ubuntu, PopOS, Archlinux) macOS, Windows
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Training and Certification}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{OWASP Appsec Day 2019}}
	      {\textbf{Melbourne, Australia}}
	      \headerrow
	      {\emph{Web Hacking Essentials}}
	      {\emph{November 2019}}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{RMIT University}}
	      {\textbf{Melbourne, Australia}}
	      \headerrow
	      {\emph{B.S. Electrical Engineering/Commerce}}
	      {\emph{March 2012 -- July 2017}}
	      	      
\end{itemize}

\hrule
\vspace{-1em}

\end{document}
